TBD

### 2016-10-11 paper.tex
paper.tex

In general, when $\bA$ is neither square, positive semi-definite or Hermitian we can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bA^H\bA\bx = \bA^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\|\bb-\bA\bx\|. 
\end{equation}
The CG method is gaurenteed to converge if we use it to solve Eq.~\eqref{eq:normal_equation}.

>>>>

In general, when $\bA$ has dimensions $m\times n$, with $m > n$ we can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bA^H\bA\bx = \bA^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bA\bx\|. 
\end{equation}
If $\bA^H\bA$ is invertiable then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bA^H\bA$ is singular there are an infinite amount of solutions
that minimizes Eq.~\eqref{eq:norm_ls}. Moreover, we can use the CG method to solve Eq.~\eqref{eq:normal_equation}, since $\bA^H\bA$ is Hermitian by construction 
and $\bA^H\bb$ is in the column range of $\bA^H\bA$.
\begin{equation}
\bA^H\bb \in \mathcal{R}(\bA^H) \implies \bA^H\bb \in \mathcal{R}(\bA^H\bA).   
\end{equation}
The CG method is gaurenteed to converge if we use it to solve Eq.~\eqref{eq:normal_equation}.
